Structural controllability of ecological networks

### 2018-06-26 paper/manuscript.Rmd
Name all code chunks

```{r}
drake::loadd(fig_struct_control)
```

@@

```{r}
drake::loadd(fig_control_config)
```

@@

```{r controllability}
drake::loadd(controllability, metadata, randomisations_test)
c_m <- controllability %>% 
  filter_networks_df(metadata)
```

@@

```{r}
drake::loadd(sl_characteristics)
crit <- sl_characteristics %>% 
  filter_networks_df(metadata) %>%
  dplyr::group_by(net_name) %>%
  dplyr::summarise(n_crit = sum(control_capacity == 1), 
                   n_sp = n()) %>%
  dplyr::mutate(p_crit = n_crit/n_sp)

>>>>

```{r load-fig-example-networks}
drake::loadd(fig_struct_control)
```

@@

```{r load-fig-control-configuration}
drake::loadd(fig_control_config)
```

@@

```{r controllability-calculations}
drake::loadd(controllability, metadata, randomisations_test)
c_m <- controllability %>% 
  filter_networks_df(metadata)
```

@@

```{r cirtical-species-descriptive}
drake::loadd(sl_characteristics)
crit <- sl_characteristics %>% 
  filter_networks_df(metadata) %>%
  dplyr::group_by(net_name) %>%
  dplyr::summarise(n_crit = sum(control_capacity == 1), 
                   n_sp = n()) %>%
  dplyr::mutate(p_crit = n_crit/n_sp)
